Improving the Replicability of Psychological Science Through Pedagogy

### 2017-08-18 paper/paper.Rmd
Update Bayes Factor footnote

Next, following @etz2016, we compared Bayes Factors between the original and replication. We used the default test suggested by @rouder2009 and did not attempt to correct for publication bias.^[This default test assumes an alternative hypothesis that the effect is present with effect size $d=.707$; a default BF for one paper could not be computed based on the statistical test that was used.] As with effect sizes, we saw generally smaller Bayes Factors for the replications than the originals (Fig. 2B). In addition, it appeared that replication Bayes Factors generally tracked nicely with subjective replication judgments. Finally, the Bayes Factors for several of the original effects did not appear to show strong evidential value (e.g., BF < 3, indicating that the alternative hypothesis was less than three times more likely than the null).

>>>>

Next, following @etz2016, we compared Bayes Factors between the original and replication. We used the default test suggested by @rouder2009 and did not attempt to correct for publication bias.^[This default test compares the null hypothesis of no effect against an alternative hypothesis placing a Cauchy prior on effect size with mean $x_0 = 0$ and scale parameter $\gamma = 1$; this distribution corresponds to a median absolute effect size of $d=1$. A default BF for one paper could not be computed based on the statistical test that was used.] As with effect sizes, we saw generally smaller Bayes Factors for the replications than the originals (Fig. 2B). In addition, it appeared that replication Bayes Factors generally tracked nicely with subjective replication judgments. Finally, the Bayes Factors for several of the original effects did not appear to show strong evidential value (e.g., BF < 3, indicating that the alternative hypothesis was less than three times more likely than the null).
